\stktokens{}: Enforcing Well-Bracketed Control Flow and Stack Encapsulation Using Linear Capabilities

### 2019-08-11 popl-2019-journal-v/proving-full-abstraction.tex
Minor fixes in discussion of LR

\caption{The trusted value relation $\lrvname_\trusted$ relates all the words that are safe for trusted components to contain. A trusted component may contain untrusted words (\figurename~\ref{fig:untrusted-val-rel}), return seals and trusted closure seals, and code pointers for trusted code. }
\label{fig:trusted-val-rel}
\end{figure}
Like the untrusted value relation, the trusted value relation is monotone.
Intuitively, the two relations are monotone for the same reason; words are potentially used at any point in time.
If words are safe now (in the current world), then they should also be safe to use later (in any possible future world).
\begin{lemma}[Trusted value relation monotonicity]
  \label{lem:monotonicity-trusted}
  For all integers $n$, words $\src{w_1}$ and $w_2$, and worlds $W' \future W$, if $\npair{(\src{w_1},w_2)} \in \lrvtrusted(W)$, then $\npair{(\src{w_1},w_2)} \in \lrvtrusted(W')$.
\end{lemma}
Another, perhaps unsurprising property, of the trusted value relation it that non-linear words do not depend on the spatial region that may be in the world.
This is unsurprising as normal capabilities do not necessarily reference memory uniquely.
\begin{lemma}[Non-linear words are independent of spatial regions]
  \label{lem:non-linear-pure}
 If $\npair{(w_1,w_2)} \in \lrvtrusted(W)$ and either $\nonLinear{w_1}$ or $\nonLinear{w_2}$, then
 \[
   \npair{(w_1,w_2)} \in \lrvtrusted(\purePart{W})
 \].
\end{lemma}
There is similar lemma to Lemma~\ref{lem:non-linear-pure} for the untrusted value relation.

>>>>

\caption{The trusted value relation $\lrvname_\trusted$ relates all the words that are safe for trusted components to contain. A trusted component may contain untrusted words (\figurename~\ref{fig:untrusted-val-rel}), return seals and trusted closure seals, and code pointers for trusted code. }
\label{fig:trusted-val-rel}
\end{figure}
Like the untrusted value relation, the trusted value relation is monotone.
Intuitively, the two relations are monotone for the same reason; words are potentially used at any point in time.
If words are safe now (in the current world), then they should also be safe to use later (in any possible future world).
\begin{lemma}[Trusted value relation monotonicity]
  \label{lem:monotonicity-trusted}
  For all integers $n$, words $\src{w_1}$ and $w_2$, and worlds $W' \future W$, if $\npair{(\src{w_1},w_2)} \in \lrvtrusted(W)$, then $\npair{(\src{w_1},w_2)} \in \lrvtrusted(W')$.
\end{lemma}
Another, perhaps unsurprising property, of the trusted value relation it that non-linear words do not depend on the spatial regions that may be in the world.
This is unsurprising as normal capabilities do not necessarily reference memory uniquely.
\begin{lemma}[Non-linear words are independent of spatial regions]
  \label{lem:non-linear-pure}
 If $\npair{(w_1,w_2)} \in \lrvtrusted(W)$ and either $\nonLinear{w_1}$ or $\nonLinear{w_2}$, then
 \[
   \npair{(w_1,w_2)} \in \lrvtrusted(\purePart{W})\text{.\qedhere}
 \]
\end{lemma}
This is similar to Lemma~\ref{lem:non-linear-pure} for the untrusted value relation.
